On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-03-27 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Acknowledgements
[AMZAE] Name correction
[AMZAE] Keywords

%% Прекрасно понимаю, что следующая команда - дичь и вордописчество, но время не ждёт, время жмёт
\author{
	Avdeev N.N.
	\footnote{nickkolok@mail.ru, avdeev@math.vsu.ru}
	, Momot E.A., Zvolinsky A.E.
	\\
	\\
	\emph{Voronezh State University}
}

@@

@@

>>>>

%% Прекрасно понимаю, что следующая команда - дичь и вордописчество, но время не ждёт, время жмёт
\author{
	Avdeev N.N.
	\footnote{nickkolok@mail.ru, avdeev@math.vsu.ru}
	, Momot E.A., Zvolinskiy A.E.
	\\
	\\
	\emph{Voronezh State University}
}

@@

\paragraph{Keywords.}
	integral point sets,
	planar integral point sets,
	classification of planar integral point sets,
	diameter of an integral point set

@@

\section{Acknowledgements}
The authors thank Dr. Prof. E.M. Semenov and Dr.~A.S.~Usachev for proofreading.
